Visualizing demographic evolution using geographically inconsistent census data

### 2019-08-10 paper/intro.tex
more regionalization

\revision{In this work, we consider neighbourhoods as \emph{formal
regions}~\citep{montello2003regions}, geographically continous areas with
similar data characteristics.} These advances have made neighbourhood constructs
more tractable to quantitative analysis. Yet new challenges have also emerged,
especially at the convergence of research on neighbourhood effects and
neighbourhood dynamics. Neighbourhood effects research assumes knowledge about
the nature and scope of "the neighbourhood" that presumably shapes individual
outcomes~\citep{Kwan2018,Shelton2019}. Concurrently, researchers note that
neighbourhoods are not necessarily fixed containers in which other processes
occur, but themselves dynamically
evolve~\citep{Delmelle2017,Reades2019,li2018new}. The result is to open up key
assumptions about neighbourhoods for theoretical and empirical examination: how
do we appropriately define and compare neighbourhoods at a given time?; how do
we appropriately define and compare the temporal trajectories of
neighbourhoods?; and can we do both at once, "fully
interactionally"~\citep{Abbott1997}: classify neighbourhoods now based on where
they came from and where they are going?

>>>>

\revision{In this work, we consider neighbourhoods as \emph{formal
regions}~\citep{montello2003regions}, geographically continous areas with
similar data characteristics, which these advances made more tractable to
approach in a data-driven fashion.} Yet new challenges have also emerged,
especially at the convergence of research on neighbourhood effects and
neighbourhood dynamics. Neighbourhood effects research assumes knowledge about
the nature and scope of "the neighbourhood" that presumably shapes individual
outcomes~\citep{Kwan2018,Shelton2019}. Concurrently, researchers note that
neighbourhoods are not necessarily fixed containers in which other processes
occur, but themselves dynamically
evolve~\citep{Delmelle2017,Reades2019,li2018new}. The result is to open up key
assumptions about neighbourhoods for theoretical and empirical examination: how
do we appropriately define and compare neighbourhoods at a given time?; how do
we appropriately define and compare the temporal trajectories of
neighbourhoods?; and can we do both at once, "fully
interactionally"~\citep{Abbott1997}: classify neighbourhoods now based on where
they came from and where they are going?

### 2019-08-10 paper/related.tex
more regionalization

Data clustering is one of the elementary processes for data analysis,
simplifying the data into a smaller number of homogeneous sets that can be
interpreted in the same way. There is no shortage of contributions for this
problem~\citep{Fahad2014}\revision{, since variations of it appear in almost all
scientific fields. Most neighbourhood related applications still rely on
k-means~\citep{jain2010data,Delmelle2016}, the Louvain method for community
detection~\citep{blondel2008Louvain,Thomas2012}, or, to a lesser extent, Self
Organising Maps~\citep{Delmelle2017,Ling2016,Dani2013_som_maxp}.}

\revision{In geography, this problem is known as
\emph{regionalisation}~\citep{montello2003regions}, a rather old problem that
has been throughly explored, leveraging different mathematical tools, including
discrete topology~\citep{brantingham1978topological} and discrete
geometry~\citep{assunccao2006efficient}. Indeed, network-based methods are among
the current state-of-the-art~\citep{Guo2008Redcap,maxp}. However,
\emph{temporal} regionalisation is significantly less explored, especially in a
demographic context, arguably due to the difficulties in dealing with
unharmonised longitudinal data.

>>>>

Data clustering is one of the elementary processes for data analysis,
simplifying the data into a smaller number of homogeneous sets that can be
interpreted in the same way. There is no shortage of contributions for this
problem~\citep{Fahad2014}\revision{, since variations of it appear in almost all
scientific fields.}

\revision{In geography, this problem is known as
\emph{regionalisation}~\citep{montello2003regions}, a rather old problem that
has been throughly explored, leveraging different mathematical tools, including
discrete topology~\citep{brantingham1978topological} and discrete
geometry~\citep{assunccao2006efficient}. Indeed, network-based methods are among
the current state-of-the-art~\citep{Guo2008Redcap,maxp}. However,
\emph{temporal} regionalisation is significantly less explored, especially in a
demographic context, arguably due to the difficulties in dealing with
unharmonised longitudinal data.   Recent neighbourhood related applications rely
on k-means~\citep{jain2010data,Delmelle2016}, the Louvain method for community
detection~\citep{blondel2008Louvain,Thomas2012}, or, to a lesser extent, Self
Organising Maps~\citep{Delmelle2017,Ling2016,Dani2013_som_maxp}, but do not
consider longitudinal data, or harmonised data.
